### 2019-03-05 README.Rmd
doc refresh

[![Documentation](https://img.shields.io/badge/Documentation-click here!-lightgrey.svg?style=flat)](https://www.samabbott.co.uk/DirectEffBCGPolicyChange)
[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/DirectEffBCGPolicyChange/master?urlpath=rstudio)
[![DOI](https://zenodo.org/badge/173767331.svg)](https://zenodo.org/badge/latestdoi/173767331)

>>>>

[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/DirectEffBCGPolicyChange/master?urlpath=rstudio)
[![Documentation](https://img.shields.io/badge/Documentation-click here!-lightgrey.svg?style=flat)](https://www.samabbott.co.uk/DirectEffBCGPolicyChange)
[![DOI](https://zenodo.org/badge/173767331.svg)](https://zenodo.org/badge/latestdoi/173767331)
